### 2016-03-10 paper/layered_depthmap.tex
yasu

\subsection{Swarm Fusion Layered Depthmap Estimation}

>>>>

\subsection{Swarm Fusion layered depthmap estimation}
Our last problem is layered depthmap estimation, recently proposed
in~\cite{layered_depthmap} (see the anonymious paper in the
supplementary material).  The problem seeks to infer layered depthmap
representation from an RGBD image, where each layer is a piecewise
smooth segmented depthmap. This is essentially a multi-layer extension
of Surface Stereo algorithm~\cite{surface_stereo}.
%
Layered depthmap estimation is one of the most difficult kinds for MAP
inference due to its massive solution space, where the number of labels
per pixel is exponential in the number of layers. In practice, each
pixel might take an order of 100,000 \yasu{is this number correc?}
possible labels. We copy their problem formulation and the proposal
generation schemes.~\footnote{Authors have proposed a novel fusion scheme,
where a solution subspace instead of a single solution is generated by a
proposal generation scheme. Since a solution subspace is equivalent to
multiple solution proposals, their algorithm can be easily integrated
into our swarm fusion framework.  However, competing fusion methods
(e.g., Parallel Fusion Move or Hierarchical Fusion) cannot handle a
solution subspace proposal, making it impossible to conduct fair
comparative evaluations. We choose to use a simple solution proposal for
experiments in this paper.}
%Lastly, we will evaluate Swarm fusion on a very challenging layered
%depthmap estimation problem~\cite{layered_depthmap}, which has been
%recently proposed (see the anonymized pdf in the supplementary
%material).

\mysubsubsection{Competing methods}

Solution proposals depend heavily on the current solution, eliminating
the possibility of using hierarchical approach, which needs to enumerate
all the proposals to start. Therefore, the only viable competing method
is Parallel Fusion Move, that replaces constant label solutions by
solution proposals in parallel alpha-expansion framework. We will also
evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

%The number of labels is extremely large (an order of 10,000 \yasu{what
%were the number of labels in our cvpr16?}), which eliminates the
%possibility of using hierarchical fusion. Therefore, we will evaluate
%fusion move and parallel fusion move algorithm as in the case of optical
%flow problem, where one solution proposal repeats being fused via QPBO.

\mysubsubsection{Swarm fusion architecture}
The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
fusions are multi-way, for which we use TRW-S.

### 2016-03-10 paper/optical_flow.tex
yasu

We use Swarm fusion to solve an optical flow problem, where a baseline
is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
Although their paper did not consider parallel implementation, it is
straightfoward to apply the concept of parallel alpha-expansion and
construct a ``parallel fusion move'' method, where multiple threads
repeat fusing two solutions via QPBO. This time, we will compare it with
our full swarm fusion model (bottom right example in
Fig.~\ref{fig:model}).

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
solve optical flow problem.
%Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and fusion proposal schemes for our second
problem.  We again use test images in the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}.

\mysubsubsection{Competing methods} Fusion Move method in their paper is
the first natural contender. While they did not consider parallel
implementation, it is straightforward to combine the idea of parallel
alpha-expansion and Fusion Move. Then, the second competing method is
``parallel fusion move'', where each thread repeats generating a
solution proposal and fusing it to the current solution. Final solutions
from all the results are sequentially fused to obtain the final solution
as in the parallel alpha-expansion method. In Fig.~\ref{fig:model}, this
computational framework corresponds to ``parallel alpha-expansion'' with
the label solutions replaced by solution proposals. The last contender
is the mix of the hierarchical fusion and the fusion move method, dubbed
``hierarchical fusion method'', where they start from solution proposals
as opposed to constant labels.
%
The fusions are binary, for which we use QPBO.

\mysubsubsection{Swarm fusion architecture}
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} will be evaluated
against the competing methods. Note that we use the same set of proposal
generation schemes. The fusions are multi-way, for which we ues TRW-S.

% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
